\subsection{Introduction}
\subsubsection{Purpose}
Rockwell Collins currently develops their vision systems on Field Programmable Gate Arrays, making the time from design to product very long.  Rockwell Collins is considering using Single Board Computers as a way to speed up this cycle.Our goal is to provide a proof of concept for a vision system on a Single Board Computer for Rockwell Collins. This proof of concept should help Rockwell Collins measure the practicality of Single Board Computers for vision systems.\\

\subsubsection{Scope}
Development will be limited to the Jetson TK1 or Jetson TX1. Evaluation of hardware platforms other than the TK1 and TX1 will be a stretch goal. In which case, these boards will serve as the base unit for comparison. Software shall interface to a minimum of 2 cameras, receive video, and display it on a monitor while logging metrics. Metrics will be frames per second and operations per second.\\

\subsubsection{Definitions}
\begin{description}[leftmargin=2cm,labelindent=2cm]
	\item [SBC] Single board computer	\item [RC] Rockwell Collins	\item [FPS] Frames per second	\item [FPGA] Field-programmable gate array	\item [USB] Universal serial bus	\item [PoC] Proof of concept	\item [SVS] Simple vision system\\
\end{description}

\subsubsection{References}
Carlo Tiana, Airborne Vision Systems Expert at Rockwell CollinsWeston Lahr, Senior Software Engineer at Rockwell Collins,Jetson TK1 Embedded Hardware, NVIDIA\\

\subsubsection{Assumptions and Constraints}
We're assuming that either Jetson model can handle some sort of camera vision system. From initial investigations it appears that the Jetson TX1 is a likely candidate to support our project goals.\\


\subsection{Overall Description}
This section will give a bird?s eye view of the project, outlining the major features and their purpose.
\subsubsection{Product Perspective}
  \paragraph{System Interfaces}
  \paragraph{User Interfaces}
  \paragraph{Software Interfaces}
  \paragraph{Hardware Interfaces}
  \paragraph{Communication Interfaces}
\subsubsection{Product Functions}
\subsubsection{User Characteristics}
\subsubsection{Constraints}
\subsubsection{Assumptions and Dependencies}
\subsubsection{Apportioning of Requirements}


\subsection{Specific Requirements}
\subsubsection{External Interfaces}
\subsubsection{Functions}
\subsubsection{Performance Requirements}
\subsubsection{Design Constraints}
\subsubsection{Maintainability}
\subsubsection{Portability}

\subsection{Gantt Chart}
