What did you learn from all this? One per team member.
What technical information did you learn?
What non-technical information did you learn?
What have you learned about project work?
What have you learned about project management?
What have you learned about working in teams?
If you could do it all over, what would you do differently?
\par
I learned a lot over the course of this project. A lot of the technical stuff with coding a GPU was framiliar territory, but coding the same ideas in different languages always helps solidify your knowledge. 
\par
I think the biggest takeaway that I got out of this project was working with a team in a long term project like this. I've worked in groups on smaller projects before but never for a whole year. In some ways working with a group for a longer amount of time is easier and in some ways it's harder. In a short project, the difficulty is learning how to work with the group in the short amount of time. When you open it up to a larger project, you realize that group projects 
\par
It was a pleasure being a part of the HawkEyed Crew from start to finish. We ended up creating a really good product together and I feel that we could do even better on future projects with the knowledge we've learned technically and being part of a team. We had a strong team dynamic and everyone did their part. No one dragged us down and the project wouldn't have been the same if someone had left. We really had a great time.
\par
In the end, I think we made a really good group together. We all brought skills to the table that others lacked and it ended up resulting in a great project. It's kinda sad to see the team break up, but maybe we'll work together in the future, who knows.
